---
title: "Demo"
author: "Lucy Chen"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:   
    pdf_document:
      toc: true
      toc_depth: 4
    fontsize: 9pt
    geometry: margin=0.25in
---

\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 0. Data Preparation
```{r warning=FALSE,  message=FALSE}

## housekeeping ##

#https://cran.r-project.org/web/packages/MatchIt/vignettes/estimating-effects.html
options("scipen"=100, "digits"=4)
rm(list=ls())

library(tidyverse) # data manipulation
library(MatchIt) # matching 
library(psych)
library(cobalt) # ploting
library(ggplot2) # ploting
library(lmtest) # robust standard error
library(sandwich) # robust standard error
library(boot) # booth-strapping unbiased confidence interval

data_path <- "C:\\Other\\AMI 2021\\data\\"
data <- readRDS(paste(data_path, "data_combined.rds", sep=""))
data_HS <- data %>% 
    filter(School_Level== "High" & TOT_ENR_M+TOT_ENR_F >0 ) %>% 
    mutate(
      SERVICES_SOC = ifelse(SCH_FTESERVICES_SOC > 2, 1, 0),
      school_size = ifelse((TOT_ENR_M+TOT_ENR_F) <150, 1, 
                        ifelse((TOT_ENR_M+TOT_ENR_F) <450, 2, 
                            ifelse((TOT_ENR_M+TOT_ENR_F) <1000, 3, 4)))) %>%
  mutate(
      # Relative Risk #
      RR_SINGOOS_F = (SCH_DISCWODIS_SINGOOS_BL_F/SCH_ENR_BL_F)/(SCH_DISCWODIS_SINGOOS_WH_F/SCH_ENR_WH_F))

```

\newpage


# 1. Presence of COUNSELORS
## 4.1 Student Discipline - Referrals to Law Enforcement (REF)
```{r}
# Matching variables
## 3. school region [region] : 4 levels: South, West, Northeast, Midwest
## 2. school social economic status [ses_sch]: 4 levels: 
##              calculated by the percentage of free and reduced lunch students
##              Low:>75% ; Middle-Low: 50%-75%; 
##              Middle-High: 25%-50%; High:: <25% 
## 3. school size [school_size]: 4 levels: Level 1: <150; Level 2 [150:499]; 
##                                         Level 3: [500:999]; Level 4: >999
## 4. total number of discipline [n_discipline]: sum of all type of discipline incidents 
## 5. total teacher FTE [SCH_FTETEACH_TOT]: 
## 6. percentage of black student at school [per_bl]:
## 7: percentage of male student at school [per_male]:
## 8: percentage of white student at school [per_wh]: 
#
# Treatment variable
## presence of social worker [COUNSELORS]: 0: none or less than 2 FTE COUNSELORS presence ; 
##                                            1: more than 2 FTE COUNSELORS presence
# Outcome Variables
##  Black  without disabilities who referrals to law enforcement [SCH_DISCWODIS_REF_BL]
##  Black Males without disabilities who referrals to law enforcement [SCH_DISCWODIS_REF_BL_M]
##  Black Female without disabilities who referrals to law enforcement [SCH_DISCWODIS_REF_BL_F]
##  White Males without disabilities who referrals to law enforcement [SCH_DISCWODIS_REF_WH_M]
##  White Female without disabilities who referrals to law enforcement [SCH_DISCWODIS_REF_WH_F]
##
### Instructions
### • Report the number of students receiving school-related arrests, not the instances of arrests.
### • School-related arrest is a subset of referral to law enforcement. 
###   Therefore, a student counted in the “school-related arrest” table 
###   should also be counted in the “referred to law enforcement agency” table.
```
\newpage

### 4.1.1 Black Female Students v.s. White Female Students
```{r}

####   data prep          #####################################################

outcome <- "RR_REF_F"
treatment <- "COUNSELORS"

data1 <- data_HS %>% select(region, ses_sch, bl_per, male_per, wh_per, 
                            school_size, n_discipline, SCH_FTETEACH_TOT,
                            !!as.name(outcome),
                            !!as.name(treatment)) %>%
                      filter(complete.cases(.) & !!as.name(outcome)> 0 & !!as.name(outcome) < 30)

####   Matching           #####################################################

m.out1 <- matchit(as.formula(paste(treatment, "~", paste("region", "ses_sch", "school_size", 
                                                         "n_discipline", "SCH_FTETEACH_TOT",
                                                         "bl_per","male_per","wh_per", sep=" + "), sep="")),
                  data = data1, caliper = 0.25)

#summary(m.out1)

m.data1 <- match.data(m.out1, data = data1)
plot(m.out1)

# covariance balance after matching  
plot_demo<- love.plot(m.out1, binary = "std", 
                      thresholds = c(m = .1),
                      abs = TRUE,
                      line = TRUE, 
                      colors = c("red", "blue"),
                      shapes = c("triangle filled", "circle filled")); plot_demo

####   Effects Analysis           ##############################################

lm_fit_matching <- lm(as.formula(paste(outcome, "~", paste(treatment, "region", "ses_sch", "school_size", 
                                                         "n_discipline", "SCH_FTETEACH_TOT",
                                                         "bl_per","male_per","wh_per", sep=" + "), sep="")), 
                  data = m.data1, weights = weights)

### with robust standard error #################################################
coeftest(lm_fit_matching, vcov. = vcovCL, cluster = ~subclass)[treatment,, drop=FALSE]


## Relative Risk ###############################################################
m.data1 %>%
  group_by(!!as.name(treatment)) %>%
  summarise(RR_mean = mean(!!as.name(outcome)))

```
\newpage

## 4.2 Student Discipline -  School-Related Arrest (ARR)
```{r}
# Matching variables
## 3. school region [region] : 4 levels: South, West, Northeast, Midwest
## 2. school social economic status [ses_sch]: 4 levels: 
##              calculated by the percentage of free and reduced lunch students
##              Low:>75% ; Middle-Low: 50%-75%; Middle-High: 25%-50%; High:: <25% 
## 3. school size [school_size]: 4 levels: Level 1: <150; Level 2 [150:499]; Level 3: [500:999]; Level 4: >999
## 4. total number of discipline [n_discipline]: sum of all type of discipline incidents 
## 5. total teacher FTE [SCH_FTETEACH_TOT]: 
## 6. percentage of black student at school [per_bl]:
## 7: percentage of male student at school [per_male]:
## 8: percentage of white student at school [per_wh]: 
#
# Treatment variable
## presence of COUNSELORS [COUNSELORS]: 0: none or less than 2 FTE COUNSELORS presence ; 
##                                            1: more than 2 FTE COUNSELORS presence
# Outcome Variables
##  Black Males without disabilities who received a school-related arrest [SCH_DISCWODIS_ARR_BL_M]
##  Black Female without disabilities who received a school-related arrest [SCH_DISCWODIS_ARR_BL_F]
##  White Males without disabilities who received a school-related arrest [SCH_DISCWODIS_ARR_WH_M]
##  White Female without disabilities who received a school-related arrest [SCH_DISCWODIS_ARR_WH_F]
##
### Instructions
### • Report the number of students receiving school-related arrests, not the instances of arrests.
### • School-related arrest is a subset of referral to law enforcement. 
###   Therefore, a student counted in the “school-related arrest” table 
###   should also be counted in the “referred to law enforcement agency” table.
```
\newpage

### 4.2.1 Black Female Students v.s. White Female Students
```{r}

####   data prep          #####################################################

outcome <- "RR_ARR_F"
treatment <- "COUNSELORS"

data1 <- data_HS %>% select(region, ses_sch, bl_per, male_per, wh_per, 
                            school_size, n_discipline, SCH_FTETEACH_TOT,
                            !!as.name(outcome),
                            !!as.name(treatment)) %>%
                      filter(complete.cases(.) & !!as.name(outcome)> 0 & !!as.name(outcome) < 30)

####   Matching           #####################################################

m.out1 <- matchit(as.formula(paste(treatment, "~", paste("region", "ses_sch", "school_size", 
                                                         "n_discipline", "SCH_FTETEACH_TOT",
                                                         "bl_per","male_per","wh_per", sep=" + "), sep="")),
                  data = data1, caliper = 0.25)

#summary(m.out1)

m.data1 <- match.data(m.out1, data = data1)

# covariance balance after matching  
plot_demo<- love.plot(m.out1, binary = "std", 
                      thresholds = c(m = .1),
                      abs = TRUE,
                      line = TRUE, 
                      colors = c("red", "blue"),
                      shapes = c("triangle filled", "circle filled")); plot_demo

####   Effects Analysis           ##############################################

lm_fit_matching <- lm(as.formula(paste(outcome, "~", paste(treatment, "region", "ses_sch", "school_size", 
                                                         "n_discipline", "SCH_FTETEACH_TOT",
                                                         "bl_per","male_per","wh_per", sep=" + "), sep="")), 
                  data = m.data1, weights = weights)

### with robust standard error #################################################
coeftest(lm_fit_matching, vcov. = vcovCL, cluster = ~subclass)[treatment,, drop=FALSE]


## Relative Risk ###############################################################
m.data1 %>%
  group_by(!!as.name(treatment)) %>%
  summarise(RR_mean = mean(!!as.name(outcome)))

```
\newpage


## 4.3 Student Discipline - In-School Suspensions (ISS)
```{r}
# Matching variables
## 3. school region [region] : 4 levels: South, West, Northeast, Midwest
## 2. school social economic status [ses_sch]: 4 levels: 
##              calculated by the percentage of free and reduced lunch students
##              Low:>75% ; Middle-Low: 50%-75%; Middle-High: 25%-50%; High:: <25% 
## 3. school size [school_size]: 4 levels: Level 1: <150; Level 2 [150:499]; Level 3: [500:999]; Level 4: >999
## 4. total number of discipline [n_discipline]: sum of all type of discipline incidents 
## 5. total teacher FTE [SCH_FTETEACH_TOT]: 
## 6. percentage of black student at school [per_bl]:
## 7: percentage of male student at school [per_male]:
## 8: percentage of white student at school [per_wh]: 
#
# Treatment variable
## presence of COUNSELORS [COUNSELORS]: 0: none or less than 2 FTE COUNSELORS presence ; 
##                                            1: more than 2 FTE COUNSELORS presence
# Outcome Variables
##  Black Males without disabilities who received a school-related ISSest [SCH_DISCWODIS_ISS_BL_M]
##  Black Female without disabilities who received a school-related ISSest [SCH_DISCWODIS_ISS_BL_F]
##  White Males without disabilities who received a school-related ISSest [SCH_DISCWODIS_ISS_WH_M]
##  White Female without disabilities who received a school-related ISSest [SCH_DISCWODIS_ISS_WH_F]
##
### Instructions
### • Report the number of students receiving school-related ISSests, not the instances of ISSests.
### • School-related ISSest is a subset of referral to law enforcement. 
###   Therefore, a student counted in the “school-related ISSest” table 
###   should also be counted in the “referred to law enforcement agency” table.
```
\newpage

### 3.3.1 Black Female Students v.s. White Female Students
```{r}

####   data prep          #####################################################

outcome <- "RR_ISS_F"
treatment <- "COUNSELORS"

data1 <- data_HS %>% select(region, ses_sch, bl_per, male_per, wh_per, 
                            school_size, n_discipline, SCH_FTETEACH_TOT,
                            !!as.name(outcome),
                            !!as.name(treatment)) %>%
                      filter(complete.cases(.) & !!as.name(outcome)> 0 & !!as.name(outcome) < 30)

####   Matching           #####################################################

m.out1 <- matchit(as.formula(paste(treatment, "~", paste("region", "ses_sch", "school_size", 
                                                         "n_discipline", "SCH_FTETEACH_TOT",
                                                         "bl_per","male_per","wh_per", sep=" + "), sep="")),
                  data = data1, caliper = 0.25)

#summary(m.out1)

m.data1 <- match.data(m.out1, data = data1)

# covariance balance after matching  
plot_demo<- love.plot(m.out1, binary = "std", 
                      thresholds = c(m = .1),
                      abs = TRUE,
                      line = TRUE, 
                      colors = c("red", "blue"),
                      shapes = c("triangle filled", "circle filled")); plot_demo

####   Effects Analysis           ##############################################

lm_fit_matching <- lm(as.formula(paste(outcome, "~", paste(treatment, "region", "ses_sch", "school_size", 
                                                         "n_discipline", "SCH_FTETEACH_TOT",
                                                         "bl_per","male_per","wh_per", sep=" + "), sep="")), 
                  data = m.data1, weights = weights)

### with robust standard error #################################################
coeftest(lm_fit_matching, vcov. = vcovCL, cluster = ~subclass)[treatment,, drop=FALSE]


## Relative Risk ###############################################################
m.data1 %>%
  group_by(!!as.name(treatment)) %>%
  summarise(RR_mean = mean(!!as.name(outcome)))

```
\newpage

## 3.4 Student Discipline -  One Out-of-School Suspension (SINGOOS)
```{r}
# Matching variables
## 3. school region [region] : 4 levels: South, West, Northeast, Midwest
## 2. school social economic status [ses_sch]: 4 levels: 
##              calculated by the percentage of free and reduced lunch students
##              Low:>75% ; Middle-Low: 50%-75%; Middle-High: 25%-50%; High:: <25% 
## 3. school size [school_size]: 4 levels: Level 1: <150; Level 2 [150:499]; Level 3: [500:999]; Level 4: >999
## 4. total number of discipline [n_discipline]: sum of all type of discipline incidents 
## 5. total teacher FTE [SCH_FTETEACH_TOT]: 
## 6. percentage of black student at school [per_bl]:
## 7: percentage of male student at school [per_male]:
## 8: percentage of white student at school [per_wh]: 
#
# Treatment variable
## presence of COUNSELORS [COUNSELORS]: 0: none or less than 2 FTE COUNSELORS presence ; 
##                                            1: more than 2 FTE COUNSELORS presence
# Outcome Variables
##  Black Males without disabilities who received One Out-of-School Suspension [SCH_DISCWODIS_SINGOOS_BL_M]
##  Black Female without disabilities who received One Out-of-School Suspension [SCH_DISCWODIS_SINGOOS_BL_F]
##  White Males without disabilities who received One Out-of-School Suspension [SCH_DISCWODIS_SINGOOS_WH_M]
##  White Female without disabilities who received One Out-of-School Suspension [SCH_DISCWODIS_SINGOOS_WH_F]
```
\newpage

### 4.4.1 Black Female Students v.s. White Female Students
```{r}

####   data prep          #####################################################

outcome <- "RR_SINGOOS_F"
treatment <- "SERVICES_SOC"

data1 <- data_HS %>% select(region, ses_sch, bl_per, male_per, wh_per, 
                            school_size, n_discipline, SCH_FTETEACH_TOT,
                            !!as.name(outcome),
                            !!as.name(treatment)) %>%
                      filter(complete.cases(.) & !!as.name(outcome)> 0 & !!as.name(outcome) < 30)

data1 %>% su

####   Matching           #####################################################

m.out1 <- matchit(RR_SINGOOS_F ~ SERVICES_SOC + region + ses_sch + school_size + 
                                      n_discipline + SCH_FTETEACH_TOT + bl_per + male_per + wh_per,
                  data = data1, caliper = 0.25)
plot(m.out1)
#summary(m.out1)

# covariance balance after matching  
plot_demo<- love.plot(m.out1, binary = "std", 
                      thresholds = c(m = .25),
                      abs = TRUE,
                      line = TRUE, 
                      colors = c("red", "blue"),
                      shapes = c("triangle filled", "circle filled")); plot_demo

# export matching data set 
m.data1 <- match.data(m.out1, data = data1)

####   Effects Analysis           ##############################################

lm_fit_matching <- lm(RR_SINGOOS_F ~ SERVICES_SOC + region + ses_sch + school_size + 
                                      n_discipline + SCH_FTETEACH_TOT + bl_per + male_per + wh_per, 
                      data = m.data1, weights = weights)

### with robust standard error #################################################
coeftest(lm_fit_matching, vcov. = vcovCL, cluster = ~subclass)[treatment,, drop=FALSE]


## Relative Risk ###############################################################
m.data1 %>%
  group_by(!!as.name(treatment)) %>%
  summarise(RR_mean = mean(!!as.name(outcome)))

```
\newpage


## 4.5 Student Discipline - More than One Out-of-School Suspension (MULTOOS)
```{r}
# Matching variables
## 3. school region [region] : 4 levels: South, West, Northeast, Midwest
## 2. school social economic status [ses_sch]: 4 levels: 
##              calculated by the percentage of free and reduced lunch students
##              Low:>75% ; Middle-Low: 50%-75%; Middle-High: 25%-50%; High:: <25% 
## 3. school size [school_size]: 4 levels: Level 1: <150; Level 2 [150:499]; Level 3: [500:999]; Level 4: >999
## 4. total number of discipline [n_discipline]: sum of all type of discipline incidents 
## 5. total teacher FTE [SCH_FTETEACH_TOT]: 
## 6. percentage of black student at school [per_bl]:
## 7: percentage of male student at school [per_male]:
## 8: percentage of white student at school [per_wh]: 
#
# Treatment variable
## presence of COUNSELORS [COUNSELORS]: 0: none or less than 2 FTE COUNSELORS presence ; 
##                                            1: more than 2 FTE COUNSELORS presence
# Outcome Variables
##  Black Males without disabilities who received More than One Out-of-School Suspension [SCH_DISCWODIS_MULTOOS_BL_M]
##  Black Female without disabilities who received More than One Out-of-School Suspension [SCH_DISCWODIS_MULTOOS_BL_F]
##  White Males without disabilities who received More than One Out-of-School Suspension [SCH_DISCWODIS_MULTOOS_WH_M]
##  White Female without disabilities who received More than One Out-of-School Suspension [SCH_DISCWODIS_MULTOOS_WH_F]
##

```
\newpage

### 3.5.1 Black Female Students v.s. White Female Students
```{r}

####   data prep          #####################################################

outcome <- "RR_MULTOOS_F"
treatment <- "COUNSELORS"

data1 <- data_HS %>% select(region, ses_sch, bl_per, male_per, wh_per, 
                            school_size, n_discipline, SCH_FTETEACH_TOT,
                            !!as.name(outcome),
                            !!as.name(treatment)) %>%
                      filter(complete.cases(.) & !!as.name(outcome)> 0 & !!as.name(outcome) < 30)

####   Matching           #####################################################

m.out1 <- matchit(as.formula(paste(treatment, "~", paste("region", "ses_sch", "school_size", 
                                                         "n_discipline", "SCH_FTETEACH_TOT",
                                                         "bl_per","male_per","wh_per", sep=" + "), sep="")),
                  data = data1, caliper = 0.25)

#summary(m.out1)

m.data1 <- match.data(m.out1, data = data1)

# covariance balance after matching  
plot_demo<- love.plot(m.out1, binary = "std", 
                      thresholds = c(m = .1),
                      abs = TRUE,
                      line = TRUE, 
                      colors = c("red", "blue"),
                      shapes = c("triangle filled", "circle filled")); plot_demo

####   Effects Analysis           ##############################################

lm_fit_matching <- lm(as.formula(paste(outcome, "~", paste(treatment, "region", "ses_sch", "school_size", 
                                                         "n_discipline", "SCH_FTETEACH_TOT",
                                                         "bl_per","male_per","wh_per", sep=" + "), sep="")), 
                  data = m.data1, weights = weights)

### with robust standard error #################################################
coeftest(lm_fit_matching, vcov. = vcovCL, cluster = ~subclass)[treatment,, drop=FALSE]


## Relative Risk ###############################################################
m.data1 %>%
  group_by(!!as.name(treatment)) %>%
  summarise(RR_mean = mean(!!as.name(outcome)))

```
\newpage


